### 2014-12-12 paper.tex
Formatting fix and another TODO

      \includegraphics[width=0.49\textwidth]{sss-moment_pop.pdf}
      \parbox[b][3in][c]{0.49\textwidth}{\caption{Plots of efficiency gap (as computed by seat share, in seats) against each compactness metric.\label{f:compactnessplots}}}
    \end{center}
  \end{figure}

@@

  %TODO(benkraft): write text for this section

>>>>

      \includegraphics[width=0.49\textwidth]{sss-moment_pop.pdf}
      \parbox[b][2.8in][c]{0.49\textwidth}{\centering \parbox{0.4\textwidth}{\caption{Plots of efficiency gap (as computed by seat share, in seats) against each compactness metric.\label{f:compactnessplots}}}}
    \end{center}
  \end{figure}

@@

  %TODO(benkraft): write text for this section
  %TODO(benkraft): add commentary on state house analyses
